
%% plan

\section{Introduction}

\section{The Abel-Jacobi map}

  \subsection{Definition}

  \subsection{Explicit bases and standard matrices}

\section{Superelliptic curves}

  %\subsection{Genus}
  \subsection{Definition \& properties}
    Content: Definition, affine model, branch points, genus, monic transform?, Riemann surface
  
  \subsection{Roots and branches of the curve}
    Content: - Complex N-th root, branches y(x), analytic continuation
  
  \subsection{Differential forms}
    Content: Thm. of Holomorphic Differential, can be taken from CN-draft
  
  \subsection{Cycles and homology}
    Content: - Definition of \alpha(a,b) and different representations
	     - Generate H_1(C,\Z)
  
\section{Strategy for the period matrix}

  \subsection{Elementary cycles}
    Content: y_{a,b}(x) defines elem. cycle \alpha(a,b), move between sheets, change of variable
  
  \subsection{Computation of periods}
    Content: Thm. Periods
  
  \subsection{Symplectic basis}
    - Sorts out relations
  
\section{Intersections}
  Content: - Def. shifting number + Thm. shifting number
	   - 4 big Lemma's for intersections
	   - Building the intersection matrix from blocks + algorithm proves rank 2g
	   - Long proof of Thm. shifting number
  
\section{Double-exponential integration}
  Content: - Thm. (Pascal)
	   - Application in our setting

\section{Computational aspects}
  Content: Winding number, computation of integration parameters, complexity analysis?


\section{Computing the Abel-Jacobi map}
  Content: - AJM bewteen branch points, 
	   - AJM between branch point an regular point,
	   - AJM between regular point and \infty,
	   
